Figure: the scatterblob

### 2022-03-31 R/scatterblob.Rmd
workable figure versions of the scatter blob

```{r}
library(readr)
scatterblob_data <- readr::read_csv("scatterblob_data.csv")
View(scatterblob_data)
```

@@

scatterblob_data$`Cognitive load` <- c(2,3,4,4.3,4.6,5,5.2,5.4,5.6,5.8,6,6.5,9,9.5)

@@

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)

svg(filename = "scatterblob_0.svg", width = 7, height = 11, bg = "white")

par(xpd = TRUE, mai = c(1.02, 0.82, 0.82, 1), bty="n")

plot(x = c(0.1,8), 
     y = c(1.1,10), 
     xlab = "Collaborativeness",
     ylab = "Technical difficulty",
     col = "white")

for (i in seq(nrow(scatterblob_data))) {
  X0 <- scatterblob_data$x1[i]
  X1 <- scatterblob_data$x2[i]
  Y <- scatterblob_data$`Cognitive load`[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
    adj_text <- -0.1
   } else {
    adj_text <- 0.5
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 20)
   text(x = median(c(X0, X1)), 
       y = Y, 
       labels = my_data$`Ways to use GitHub`[i],
       adj = adj_text)
}
dev.off()
```
![Fgure 1. Degree of collaboration VS technical difficulty](scatterblob_0.svg)

@@

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)

svg(filename = "scatterblob.svg", width = 7, height = 9, bg = "white")
par(xpd = TRUE, mai = c(1.02, 0.82, 0.82, 2), bty="n")
plot(x = c(0.1,6), 
     y = c(0.1,15), 
     xlab = "Collaborativeness",
     ylab = "Technical difficulty",
     col = "white")

for (i in seq(nrow(scatterblob_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
    adj_text <- -0.1
   } else {
    adj_text <- 0.5
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 40)
   text(x = median(c(X0, X1)), 
       y = Y, 
       labels = my_data$`Ways to use GitHub`[i],
       adj = adj_text)
}
dev.off()
```

![Figure 2. Degree of collaboration VS Even technical difficulty](scatterblob.svg)

>>>>

```{r}
library(readr)
scatterblob_data <- readr::read_csv("scatterblob_data.csv")
library(googlesheets4)
scatterblob_data <- googlesheets4::read_sheet(ss = "https://docs.google.com/spreadsheets/d/1Ls0DofQWSZQsqtP4OLFj326sGfWsklrI2tA1GNUTR6g/edit?pli=1#gid=0")

View(scatterblob_data)

```

@@

@@

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
###############################################################
# start the pdf connection and set graphical parameters
###############################################################
pdf(file = "scatterblob_0.pdf", 
    width = 8.25, 
    height = 6, 
    bg = "transparent")
par(xpd = NA, 
    mai = c(1.02, 1, 0.82, 4), 
    bty="n")
###############################################################
# create the plot background
###############################################################
plot(x = c(0.5, 5.5), 
     y = c(1.75, 9.75), 
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02) 
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(1, rep(1.05, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "The \ncommunity", 
                "The \npublic"))
text(x = c(1, 3, 5),
     y = 0.5, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(2, 4, 6, 8, 10), 
     cex = 0.7,
     adj = 1,
     labels = c("Elementary", 
                "Low \nintermediate", 
                "Intermediate", 
                "Pre- \nAdvanced", 
                "Very \nAdvanced"))
###############################################################
# plot scatter blobs
###############################################################
for (i in seq(nrow(scatterblob_data))) {
  X0 <- scatterblob_data$x1[i]
  X1 <- scatterblob_data$x2[i]
  Y <- scatterblob_data$`Cognitive load`[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 13)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = scatterblob_data$`Cognitive load`, 
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```
![Figure 1. Degree of collaboration VS technical difficulty](scatterblob_0.pdf)

@@

```{r}
my_colors <- viridis::turbo(n = nrow(scatterblob_data), alpha = 0.9)
###############################################################
# start the pdf connection and set graphical parameters
###############################################################
pdf(file = "scatterblob_1.pdf", 
    width = 8.25, 
    height = 6, 
    bg = "transparent")
par(xpd = NA, 
    mai = c(1.02, 1, 0.82, 4), 
    bty="n")
plot(x = c(0.5, 5.5), 
     y = c(0.5, 14), 
     xlab = "",
     ylab = "",
     col = "white",
     # "hide" the tick labels so we can put some words instead of numbers:
     col.axis = "white",
     tck = 0.02) 
title(ylab="Technical difficulty", line=4, cex.lab=1)
title(xlab="Degree of collaborativeness", line= 3.5, cex.lab=1)
###############################################################
# add tick labels
###############################################################
text(x = 1:5,
     y = c(-0.65, rep(-0.7, 4)), 
     cex = 0.7,
     labels = c("Personal", 
                "Lab \nmembers", 
                "Other \nlabs", 
                "The \ncommunity", 
                "The \npublic"))
text(x = c(1, 3, 5),
     y = -1.7, 
     labels = c("Low", "Medium", "High"))
# Technical difficulty levels from https://www.londonschool.com/level-scale/
text(x = 0.2,
     y = c(0, 2, 4, 6, 8, 10, 12, 14), 
     cex = 0.7,
     adj = 1,
     labels = c("Beginner",
                "Elementary", 
                "Low\nintermediate",
                "Pre-\nintermediate",
                "Intermediate", 
                "Upper\nintermediate",
                "Pre-\nAdvanced", 
                "Very\nAdvanced"))
###############################################################
# plot scatter blobs on sequential cognitive load
###############################################################
for (i in seq(nrow(scatterblob_data))) {
  X0 <- my_data$x1[i]
  X1 <- my_data$x2[i]
  Y <- my_data$y[i]
  if (X0 == X1) {
    X0 <- X0 - 0.01
    X1 <- X1 + 0.01
   }
  segments(x0 = X0,
           x1 = X1,
           y0 = Y,
           col = my_colors[i],
           lwd = 23)
}
###############################################################
# add github uses text
###############################################################
text(x = 5.5,
    y = my_data$y, 
    labels = my_data$`Ways to use GitHub`,
    adj = 0,
    col = my_colors)
dev.off()
```

![Figure 2. Degree of collaboration VS Even technical difficulty](scatterblob_1.pdf)
